---
title: "Block Analytics Report"
author: "Block Inc."
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: null
    highlight: tango
    css: !expr gooseR::brand_css_inline()
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.width = 7,
  fig.height = 5,
  fig.align = 'center'
)

# Load libraries
library(ggplot2)
library(gooseR)

# Set brand theme as default
theme_set(theme_brand("block"))

# Load brand colors
brand_colors <- brand_palette("block", "categorical")
```

# Executive Summary

Key findings and recommendations go here.

# Introduction

Background and context for the analysis.

# Methods

Description of data sources and analytical approach.

# Results

## Data Overview

```{r example-plot}
# Example plot with brand theme
ggplot(mtcars, aes(x = mpg, y = wt, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_manual(values = brand_palette("block", "categorical", 3)) +
  labs(
    title = "Fuel Efficiency vs Weight",
    subtitle = "By number of cylinders",
    x = "Miles per Gallon",
    y = "Weight (1000 lbs)",
    color = "Cylinders"
  )
```

# Discussion

Interpretation of results and implications.

# Conclusions

Summary of key findings and next steps.

# Appendix

Additional tables, figures, and technical details.
